Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-11-01 paper/ms.tex
update ms

% upon AAS submission
%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
% drafting / arxiv
%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
%\turnoffedit

@@

\received{2023 September 8}
\revised{---}
\accepted{---}
\shorttitle{Four Years of Complex Periodic Variables}

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  Given our selection criteria for the stars,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{U}(2000, 8000), \\
  R_\star / R_\odot  &\sim \mathcal{U}(0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
truncated normal distribution with mean $\mu$, standard deviation
$\sigma$, and lower and upper bounds $a$ and $b$.  We validated our
chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
sampled the posterior probability assuming the default Gaussian
likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
0.01$, where $\mathcal{Z}$ denotes the evidence.

@@

\added{To explore the proximity of the dip and spot periods, we
generated synthetic light curves that superposed a sinusoid and a single
eclipse.  We imposed periods, amplitudes, sampling, and noise properties
similar to typical CPVs in Figure~\ref{fig:cpvs}.  We then tuned
the period of the eclipse signal to differ slightly from the
sinusoidal period, and processed the resulting synthetic signals
through the same period-finding routine to which we subjected the real data.
Provided the dip and sinusoid periods agreed to within $\approx$0.1\%, we found that
phase-folding on the dominant period (that of the larger-amplitude starspots)
yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However,
increasing the period difference beyond $\gtrsim$0.3\%, the dip signal quickly becomes
``smeared'' out and unidentifiable when phase-folding.  This
exercise highlights that our search was sensitive only to stars with dip
and spot periods that agreed to within a few parts per thousand.  
Some CPVs may exceed this threshold; we encourage
future work aimed at determining whether such stars exist.}

>>>>

% upon AAS submission
\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
% drafting / arxiv
%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
%\turnoffedit

@@

\received{2023 September 8}
\revised{2023 November 3}
\accepted{---}
\shorttitle{Four Years of Complex Periodic Variables}

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  Given our selection criteria for the stars,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{U}(2000, 8000), \\
  R_\star / R_\odot  &\sim \mathcal{U}(0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for \deleted{$\mathcal{N}$ the Gaussian and }$\mathcal{U}$ the uniform
distribution\deleted{s, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
truncated normal distribution with mean $\mu$, standard deviation
$\sigma$, and lower and upper bounds $a$ and $b$}.  We validated our
chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
sampled the posterior probability assuming the default Gaussian
likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
0.01$, where $\mathcal{Z}$ denotes the evidence.

@@

\added{To explore the proximity of the dip and spot periods, we
generated synthetic light curves that superposed a sinusoid and a single
eclipse.  We imposed periods, amplitudes, sampling, and noise properties
similar to typical CPVs in Figure~\ref{fig:cpvs}.  We then tuned
the period of the eclipse signal to differ slightly from the
sinusoidal period, and processed the resulting synthetic signals
through the same period-finding routine to which we subjected the real data.
Provided the dip and sinusoid periods agreed to within $\approx$0.1\%, we found that
phase-folding on the dominant period (that of the larger-amplitude starspots)
yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However,
increasing the period difference beyond $\gtrsim$0.3\%, the dip signal quickly becomes
``smeared'' out and unidentifiable when phase-folding.  This
exercise highlights that our search was sensitive only to stars with dip
and spot periods that agreed to within a few parts per thousand.  
Some CPVs may exceed this threshold; we encourage
future work aimed at determining whether such systems exist.}
